Listening Effort MSC Analysis

### 2024-02-12 MSC 2024 Analysis/msc_analysis.Rmd
pupil dilation analysis

>>>>

## Pupil Dilation Models

### Unconditional Growth Curve Model

# Getting region of interest for analysis
data_roi <- data |>
  # filtering out timebins below 500 (i.e., keeping timebins above 500 ms)
  dplyr::filter(time_norm >= 500) |>
  dplyr::group_by(subject, trial) |>
  # filtering out timebins 1000 ms after phrase offset
  dplyr::filter(time_norm<= max(time_norm) - 2000) |>
  ungroup()

# Adding linear, quadratic, and cubic orthogonal polynomials to the df
data_roi <- gazer::code_poly(data_roi, predictor = "time_norm", poly.order = 3, orthogonal = T, draw.poly = F)

# Unconditional Growth Model
m0 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 +
                (poly1 + poly2 + poly3|subject) + (poly1 + poly2 + poly3|code), 
              data = data_roi)

sjPlot::tab_model(m0, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term"),
                  dv.labels = "Pupil Dilation")

# Running into convergence issues, so removed the random effects for phrase (i.e. code)
m1 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker +
                (poly1 + poly2 + poly3|subject), 
              data = data_roi)

sjPlot::tab_model(m1, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]"),
                  dv.labels = "Pupil Dilation")

m2 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                (poly1 + poly2 + poly3|subject), 
              data = data_roi)

sjPlot::tab_model(m2, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]"),
                  dv.labels = "Pupil Dilation")

m3 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 +
                (poly1 + poly2 + poly3|subject), 
              data = data_roi)

sjPlot::tab_model(m3, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term"),
                  dv.labels = "Pupil Dilation")

### Model 4

m4 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 + speaker*poly2 +
                (poly1 + poly2 + poly3|subject), 
              data = data_roi)

sjPlot::tab_model(m4, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term",
                                      "Speaker [ALS] * Quadratic Term"),
                  dv.labels = "Pupil Dilation")

m5 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 + speaker*poly2 + speaker*poly3 +
                (poly1 + poly2 + poly3|subject), 
              data = data_roi)

sjPlot::tab_model(m5, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term",
                                      "Speaker [ALS] * Quadratic Term", "Speaker [ALS] * Cubic Term"),
                  dv.labels = "Pupil Dilation")

m6 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 + speaker*poly2 + speaker*poly3 + speaker*rep_acc +
                (poly1 + poly2 + poly3|subject), 
              data = data_roi)

sjPlot::tab_model(m6, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term",
                                      "Speaker [ALS] * Quadratic Term", "Speaker [ALS] * Cubic Term", 
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]"),
                  dv.labels = "Pupil Dilation")

```
### Model 7

m7 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 + speaker*poly2 + speaker*poly3 + speaker*rep_acc +
                rep_acc*poly1 +
                (poly1 + poly2 + poly3|subject), 
              data = data_roi)

sjPlot::tab_model(m7, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term",
                                      "Speaker [ALS] * Quadratic Term", "Speaker [ALS] * Cubic Term", 
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Linear Term"),
                  dv.labels = "Pupil Dilation")

m8 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 + speaker*poly2 + speaker*poly3 + speaker*rep_acc +
                rep_acc*poly1 + rep_acc*poly2 +
                (poly1 + poly2|subject), 
              data = data_roi)

sjPlot::tab_model(m8, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term",
                                      "Speaker [ALS] * Quadratic Term", "Speaker [ALS] * Cubic Term", 
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Linear Term", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Quadratic Term"),
                  dv.labels = "Pupil Dilation")

### Model 9

m9 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 + speaker*poly2 + speaker*poly3 + speaker*rep_acc +
                rep_acc*poly1 + rep_acc*poly2 + rep_acc*poly3 +
                (poly1 + poly2|subject), 
              data = data_roi)

sjPlot::tab_model(m9, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term",
                                      "Speaker [ALS] * Quadratic Term", "Speaker [ALS] * Cubic Term", 
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Linear Term", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Quadratic Term",
                                      "Phrase Repetition Accuracy [Inaccurate] * Cubic Term"),
                  dv.labels = "Pupil Dilation")

anova(m8, m9)

```
### Model 10

m10 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 + speaker*poly2 + speaker*poly3 + speaker*rep_acc +
                rep_acc*poly1 + rep_acc*poly2 + rep_acc*poly3 +
                speaker*rep_acc*poly1 +
                (poly1 + poly2|subject), 
              data = data_roi)

sjPlot::tab_model(m10, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term",
                                      "Speaker [ALS] * Quadratic Term", "Speaker [ALS] * Cubic Term", 
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Linear Term", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Quadratic Term",
                                      "Phrase Repetition Accuracy [Inaccurate] * Cubic Term",
                                      "Speaker * Phrase Repetition Accuracy * Linear Term"),
                  dv.labels = "Pupil Dilation")

anova(m9, m10)

```
### Model 11

m11 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 + speaker*poly2 + speaker*poly3 + speaker*rep_acc +
                rep_acc*poly1 + rep_acc*poly2 + rep_acc*poly3 +
                speaker*rep_acc*poly1 + speaker*rep_acc*poly2 +
                (poly1 + poly2|subject), 
              data = data_roi)

sjPlot::tab_model(m11, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term",
                                      "Speaker [ALS] * Quadratic Term", "Speaker [ALS] * Cubic Term", 
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Linear Term", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Quadratic Term",
                                      "Phrase Repetition Accuracy [Inaccurate] * Cubic Term",
                                      "Speaker * Phrase Repetition Accuracy * Linear Term",
                                      "Speaker * Phrase Repetition Accuracy * Quadratic Term"),
                  dv.labels = "Pupil Dilation")

anova(m10, m11)

```
### Model 12

m12 <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 + speaker*poly2 + speaker*poly3 + speaker*rep_acc +
                rep_acc*poly1 + rep_acc*poly2 + rep_acc*poly3 +
                speaker*rep_acc*poly1 + speaker*rep_acc*poly2 + speaker*rep_acc*poly3 +
                (poly1 + poly2|subject), 
              data = data_roi)

sjPlot::tab_model(m12, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term",
                                      "Speaker [ALS] * Quadratic Term", "Speaker [ALS] * Cubic Term", 
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Linear Term", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Quadratic Term",
                                      "Phrase Repetition Accuracy [Inaccurate] * Cubic Term",
                                      "Speaker * Phrase Repetition Accuracy * Linear Term",
                                      "Speaker * Phrase Repetition Accuracy * Quadratic Term",
                                      "Speaker * Phrase Repetition Accuracy * Cubic Term"),
                  dv.labels = "Pupil Dilation")

anova(m11, m12)

### Final Model

final_model <- glmmTMB(normed_pupil ~ poly1 + poly2 + poly3 + speaker + rep_acc +
                speaker*poly1 + speaker*poly2 + speaker*poly3 + speaker*rep_acc +
                rep_acc*poly1 + rep_acc*poly2 + rep_acc*poly3 +
                speaker*rep_acc*poly1 + speaker*rep_acc*poly2 +
                (poly1 + poly2|subject), 
              data = data_roi)

sjPlot::tab_model(final_model, pred.labels = c("Intercept", "Linear Term", "Quadratic Term", "Cubic Term", "Speaker [ALS]",
                                      "Phrase Repetition Accuracy [Inaccurate]", "Speaker [ALS] * Linear Term",
                                      "Speaker [ALS] * Quadratic Term", "Speaker [ALS] * Cubic Term", 
                                      "Speaker [ALS] * Phrase Repetition Accuracy [Inaccurate]", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Linear Term", 
                                      "Phrase Repetition Accuracy [Inaccurate] * Quadratic Term",
                                      "Phrase Repetition Accuracy [Inaccurate] * Cubic Term",
                                      "Speaker * Phrase Repetition Accuracy * Linear Term",
                                      "Speaker * Phrase Repetition Accuracy * Quadratic Term"),
                  dv.labels = "Pupil Dilation", 
                  file = "Tables/pupil_dilation_model.html")
